Batch, Off-Policy Apprencticeship Learning

### 2011-03-28 main.tex
Conclusion

\section{LSTD-$\mu$}
Let us write the definition of the $i^\text{th}$ component of a
feature expectation $\mu^\pi(s)$ for some policy $\pi$:
\begin{equation}
  \mu_i^\pi(s) = E[\sum_{t=0}^\infty \gamma^t \phi_i(s_t)|s_0=s,\pi]
  \label{eqn:phi}
\end{equation}
This is exactly the definition of the value function of the policy
$\pi$ for the MDP considered with the $i^\text{th}$ basis function
$\phi_i(s)$ as the reward function. There exists many algorithms to
estimate a value function, any of them can be used to estimate
$\mu_i^\pi$. Based on this remark, we propose to use specifically
the least-squares temporal difference (LSTD)
algorithm~\citep{bradtke1996linear} to estimate each component of the
feature expectation (as each of these components can be understood
as a value function related to a specific and known reward
function).

@@

It shall be noted that although it plays its role, the halt criterion is not a good measure of the quality of the current policy in mc\_ANIRL either, as it can be low when the policy is bad. The best policy, however, can be easily chosen from the $||\mu(s_0) - \mu_E(s_0)||_2$ term, which mc\_ANIRL can compute. When this term is low, the objective performance (that is, $V^E(s_0)-V^\pi(s_0)$ with respect to the unknow true reward function) is low too. 
\begin{figure}
\includegraphics[width=.5\textwidth]{../Code/courbe_e.pdf}
\caption{$||\mu_E(s_0)-\mu_\pi(s_0)||_2$ with respect to the number of samples available from the expert. Our algorithm is not as good as \citet{abbeel2004apprenticeship} with very few samples, but make up for it very soon.}
\label{fig:E}
\end{figure}
\label{sec:perf}
\begin{figure}
\includegraphics[width=.5\textwidth]{../Code/courbe_a.pdf}
\caption{Different criteria with respect to the number of iterations for a run of mc\_ANIRL.}
\label{fig:A}
\end{figure}
\begin{figure}
\includegraphics[width=.5\textwidth]{../Code/courbe_b.pdf}
\caption{Different criteria with respect to the number of samples from the expert, for several runs of lstd\_ANIRL.}
\label{fig:B}
\end{figure}
\section{Conclusion}

\label{sec:conclusion}
\bibliographystyle{named}
\bibliography{../Biblio/Biblio}
\end{document}

>>>>

\section{LSTD-$\mu$}
\label{sec:lstdmu}
Let us write the definition of the $i^\text{th}$ component of a
feature expectation $\mu^\pi(s)$ for some policy $\pi$:
\begin{equation}
  \mu_i^\pi(s) = E[\sum_{t=0}^\infty \gamma^t \phi_i(s_t)|s_0=s,\pi]
  \label{eqn:phi}
\end{equation}
This is exactly the definition of the value function of the policy
$\pi$ for the MDP considered with the $i^\text{th}$ basis function
$\phi_i(s)$ as the reward function. There exists many algorithms to
estimate a value function, any of them can be used to estimate
$\mu_i^\pi$. Based on this remark, we propose to use specifically
the least-squares temporal difference (LSTD)
algorithm~\citep{bradtke1996linear} to estimate each component of the
feature expectation (as each of these components can be understood
as a value function related to a specific and known reward
function).

@@

It shall be noted that although it plays its role, the halt criterion is not a good measure of the quality of the current policy in mc\_ANIRL either, as it can be low when the policy is bad. The best policy, however, can be easily chosen from the $||\mu(s_0) - \mu_E(s_0)||_2$ term, which mc\_ANIRL can compute. When this term is low, the objective performance (that is, $V^E(s_0)-V^\pi(s_0)$ with respect to the unknow true reward function) is low too. 
\section{Conclusion}
\label{sec:conclusion}
Given some transitions generated by an expert controlling a system and maximizing in the long run an unknown reward, we ported \citet{abbeel2004apprenticeship}'s approach to apprenticeship learning vie inverse reinforcement learning to a batch, model-free, off-policy setting at the cost of the need for a bigger number of samples from the expert. We believe this cost is not prohibitive as our approach only requires isolated samples which are often less difficult to get than whole trajectories as needed by the original approach. Furthermore, our method requires less computing power as it converges after only one iteration (that is, as far as we witnessed in our experimental setting).\\

The simple idea of using LSTD to estimate the feature expectation can be applied to other algorithms as well, for example \cite{abbeel2004apprenticeship,syed2008apprenticeship,syed2008game,ziebart2008maximum}.\\

The exact reason why LSTD$\mu$ converges so fast should be investigated and a bigger experiment should be run, possibly on a continuous problem.\\
\begin{figure}
\includegraphics[width=.5\textwidth]{../Code/courbe_e.pdf}
\caption{$||\mu_E(s_0)-\mu_\pi(s_0)||_2$ with respect to the number of samples available from the expert. Our algorithm is not as good as \citet{abbeel2004apprenticeship} with very few samples, but make up for it very soon.}
\label{fig:E}
\end{figure}
\label{sec:perf}
\begin{figure}
\includegraphics[width=.5\textwidth]{../Code/courbe_a.pdf}
\caption{Different criteria with respect to the number of iterations for a run of mc\_ANIRL.}
\label{fig:A}
\end{figure}
\begin{figure}
\includegraphics[width=.5\textwidth]{../Code/courbe_b.pdf}
\caption{Different criteria with respect to the number of samples from the expert, for several runs of lstd\_ANIRL.}
\label{fig:B}
\end{figure}
\bibliographystyle{named}
\bibliography{../Biblio/Biblio}
\end{document}
